Conditional selectivity for Hexastores

### 2011-07-20 conditional/trunk/selectivity-hexastore.tex
eq formating
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@17 43ef1190-90fd-4dd7-a769-d0121f02b80e

From elementary statistics, we know that the intersection probability
can be written as
\begin{equation}
Pr(A_1 \cap A_2  \cap \ldots \cap A_n) = 
  Pr(A_n | A_1 \cap A_2  \cap \ldots \cap A_{n-1}) \\
  \cdot Pr(A_{n-1} | A_1 \cap A_2  \cap \ldots \cap A_{n-2}) 
  \cdot \ldots \cdot Pr(A_2 | A_1) \cdot Pr(A_1) ,
\end{equation}
where the $|$ symbol is read as ``given'', e.g. ``given a predicate
\rdfterm{rdf:type} what is the probability that the object is \rdfterm{foaf:Person}?''

>>>>

From elementary statistics, we know that the intersection probability
can be written as
\begin{eqnarray}
Pr(A_1 \cap A_2  \cap \ldots \cap A_n) &=& 
  Pr(A_n | A_1 \cap A_2  \cap \ldots \cap A_{n-1}) \nonumber\\
  &&\cdot Pr(A_{n-1} | A_1 \cap A_2  \cap \ldots \cap A_{n-2}) \cdot \ldots \nonumber\\
  && \cdot Pr(A_2 | A_1) \cdot Pr(A_1) ,
\end{eqnarray}
where the $|$ symbol is read as ``given'', e.g. ``given a predicate
\rdfterm{rdf:type} what is the probability that the object is \rdfterm{foaf:Person}?''
